Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

{ 
(ok)Result 改寫 CAMK2N1, IL19; 
Supplementary;
Discussion:
([ok] 3.2, 3.3 只留下 validated by GSE2837)
(ok) Figure_4_CAMK2N1_IL19.pdf  KM plots
(ok)table 1 (6 genes), (ok) table 2 (4 genes)

\resizebox{\linewidth}{!}{ % adjust table size to fit the page width
Table 3: CAMK2N1 (ok)
Table 4: IL19  (ok)
\label
}

six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
}

@@

We appreciate the reviewer for the critical comments.
*** => a gene signature with deep learning CNN
https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z

https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8

@@

% 不要誇大說明 謙虛道歉
=> We are apology for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.

@@

\begin{outline}
\1 including null expressed genes, over 50\% of the cohort, 
\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
{
[main_marginSFP_HNSCC.R] line 1361
=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
OS_live_days /30 # derived from last followup [30]/ last known alive [31])
event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
R help from Jorge I Velez
[line 1654]
=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
# SLC35E2A: 9906
# SLC35E2B: 728661
}
\end{outline}

>>>>

%%{
(ok)Result altered to CAMK2N1, IL19; 
Supplementary;
Discussion:
([ok] 3.2, 3.3 remained validated by GSE2837)
(ok) new Figure4.pdf  KM plots
(ok)table 1 (6 genes), (ok) table 2 (4 genes)

Table 3: CAMK2N1 (ok)
Table 4: IL19  (ok)

six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%%}

@@

We appreciate the reviewer for the critical comments.
*** => a gene signature with deep learning CNN
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z

%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8

@@

Answer

% 不要誇大說明 謙虛道歉
We are apology for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.

@@

\begin{outline}
\1 including null expressed genes, over 50\% of the cohort, 
\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 to 20500).
%

%[main\_marginSFP\_HNSCC.R] line 1361
osccT_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
event (alive) to censored (status 0) % to handle missing data of censored by OS_months imputation
R help from Jorge I Velez
[line 1654]
for gene correction (20499 to 20500) from SLC35E2A to 2 genes:
% SLC35E2A: 9906
% SLC35E2B: 728661
\end{outline}
